Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-09 text/src/article.tex
Fix spacing in title address
Fix incorrect quotes

\address{\iid(1) Department of Biological Sciences, Northern Kentucky%
University, Nunn Drive, Highland Heights, KY 41076 }%

@@

@@

The last entry adds the sequence 'sequence2' in the scaffold file. This entry
demonstrates three further attributes for a sequence entry.The `start' and
`stop' tags are used to trim the sequence used in the scaffold to these
coordinates inclusively. The ``reverse'' tag is used to reverse complement this
region in the final super sequence. \pb

@@

% }}}
\section*{Authors contributions} %{{{1
  The authors declare no competing interests.

>>>>

\address{\iid(1) Department of Biological Sciences, Northern Kentucky %
University, Nunn Drive, Highland Heights, KY 41076 }%

@@

\clearpage

@@

The last entry adds the sequence `sequence2' in the scaffold file. This entry
demonstrates three further attributes for a sequence entry.The `start' and
`stop' tags are used to trim the sequence used in the scaffold to these
coordinates inclusively. The ``reverse'' tag is used to reverse complement this
region in the final super sequence. \pb

@@

\clearpage

\section*{Authors contributions} %{{{1
  The authors declare no competing interests.
